Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-23 paper.tex
a few more edits to the intro

\pfcomment{Banguri, I'm a bit confused about the citizen science application --- let's leave it out of the dissertation, but leave it in the paper.  Can you add some more detail?  For example, with Galaxy Zoo, my understanding is that you are looking at galaxies on a computer screen and so there is no weather.  Maybe you are talking about e-bird?  Can you write something that clarifies this and then we can talk more?}

@@

\pfcomment{Bangrui, if you can come up with an example of an application with implicit attribute feedback, include it here.}

@@

@@

\section{Related Work}

We broadly categorize the literature into two categories based on whether there is money transfer.

With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore. In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget. \cite{han2015incentivizing} generalizes this framework to allow agents have heterogeneous value of money. Further, it assumes there is a external signal scheme which provides partial information about each agent. Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.

Without money transfer but using information asymmetry: \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time. \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time. \cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and allow agents to interact with each other. In these papers, the principal provides each agent an recommendation at each time, which is Bayesian incentive-compatible. They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.

>>>>

@@

\pfcomment{Banguri, I'm a bit confused about the citizen science application --- let's leave it out of the dissertation, but leave it in the paper.  Can you add some more detail?  For example, with Galaxy Zoo, my understanding is that you are looking at galaxies on a computer screen and so there is no weather.  Maybe you are talking about e-bird?  Can you write something that clarifies this and then we can talk more?
Also, if you can come up with an example of an application with implicit attribute feedback, include it here.}

@@

We broadly categorize the literature into two categories based on whether there is money transfer.
With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore. In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget. \cite{han2015incentivizing} generalizes this framework to allow agents have heterogeneous value of money. Further, it assumes there is a external signal scheme which provides partial information about each agent. Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.

Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time. \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time. \cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and allow agents to interact with each other. In these papers, the principal provides each agent an recommendation at each time, which is Bayesian incentive-compatible. They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.

@@
